---
title: "QuantCrit in Undergraduate Mathematics"
always_allow_html: true
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
    theme: flatly
    self_contained: yes
    mode: selfcontained
  pdf_document:
    toc: false
    toc_depth: 2
    number_section: true 
  word_document: 
    fig_caption: true
geometry: margin=1.0in
editor_options:
  markdown:
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, # By default, hide code; set to TRUE to see code
  fig.pos = 'th', # Places figures at top or here
  out.width = '100%', dpi = 300, # Figure resolution and size
  fig.env="figure"
) # Latex figure environment

# install.packages("bibliometrix")
library(bibliometrix)

layout="l-body-outset"
library(rmarkdown)

options(knitr.table.format = "latex") # For kable tables to write LaTeX table directly
```

```{r, include=F, warning=F}
## set up, load libraries
library(dplyr)
library(readtext)
library(tidyverse)
library(here)
library(gt)
library(ggplot2)
library(dplyr)
library(knitr)
library(kableExtra)
here::i_am("quant-crit-math.Rmd")
```

# Overview

The purpose of this document is to prepare a systematic process to outline and understand the literature on critical quantification in relation to mathematics education. We provide an overview of the scoping process of the peer-reviewed research literature related to critical quantification in undergraduate mathematics, with a focus on general education courses. The scoping process was conducted in the Web of Science platform, which allows users to search for indexed articles through a series of queries. For this project, queries were run in relation to the following keywords: *Undergraduate, Mathematics, QuantCrit, General education, critical, quantification*

# Scoping

## First pass

An initial search using two keywords "undergraduate mathematics" and "critquant" returned only one (1) article:

Rios, J. (2024). Language, comfort speaking, and collaboration: A QuantCrit analysis of multilingual students’ experiences in introductory college mathematics courses. International Journal of Research in Undergraduate Mathematics Education, 10(2), 642-672.

## Second pass

During a second pass, we remove the term "undergraduate" from "undergraduate mathematics" and retain the keyword "critquant"; this search returned a total of six (6) articles. These articles can be viewed below:

```{r}
# load wos second pass results
library(readr)
pass2 <- readtext(here("data/savedrecs_math_quantcrit.txt"))
# query: https://www.webofscience.com/wos/woscc/summary/d7af3b36-f07b-483c-b4a4-88106c39f6aa-012a425b6f/relevance/1
pass2
```

```{r}
# convert file to a bibliometric df
P2 <- convert2df(file=pass2, dbsource= "wos", format= "plaintext")
P2 # view data
```
